### 2014-07-22 MS.tex
ä
ã

7. Heikkilä M, Kaila L, Mutanen M, Pe\~na C, Wahlberg N (2012) Cretaceous
origin and repeated tertiary diversification of the redefined
butterflies. P Roy Soc B 279: 1093--1099.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.1430}{10.1098/rspb.2011.1430}.

8. Elias M, Joron M, Willmott KR, Silva-Brandão KL, Kaiser V, et al.
(2009) Out of the Andes: Patterns of diversification in clearwing
butterflies. Mol Ecol 18: 1716--1729.
doi:\href{http://dx.doi.org/10.1111/j.1365-294X.2009.04149.x}{10.1111/j.1365-294X.2009.04149.x}.

@@

26. Silva-Brandão KL, Wahlberg N, Francini RB, Azeredo-Espin AML, Brown
Jr. KS, et al. (2008) Phylogenetic relationships of butterflies of the
tribe Acraeini (Lepidoptera, Nymphalidae, Heliconiinae) and the
evolution of host plant use. Mol Phylogenet Evol 46: 515--531.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2007.11.024}{10.1016/j.ympev.2007.11.024}.

@@

43. Brower AVZ, Freitas AVL, Lee M-M, Silva-Brandão KL, Whinnett A, et
al. (2006) Phylogenetic relationships among the Ithomiini (Lepidoptera:
Nymphalidae) inferred from one mitochondrial and two nuclear gene
regions. Syst Entomol 31: 288--301.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2006.00321.x}{10.1111/j.1365-3113.2006.00321.x}.

>>>>

7. Heikkil\"a M, Kaila L, Mutanen M, Pe\~na C, Wahlberg N (2012) Cretaceous
origin and repeated tertiary diversification of the redefined
butterflies. P Roy Soc B 279: 1093--1099.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.1430}{10.1098/rspb.2011.1430}.

8. Elias M, Joron M, Willmott KR, Silva-Brand\~ao KL, Kaiser V, et al.
(2009) Out of the Andes: Patterns of diversification in clearwing
butterflies. Mol Ecol 18: 1716--1729.
doi:\href{http://dx.doi.org/10.1111/j.1365-294X.2009.04149.x}{10.1111/j.1365-294X.2009.04149.x}.

@@

26. Silva-Brand\~ao KL, Wahlberg N, Francini RB, Azeredo-Espin AML, Brown
Jr. KS, et al. (2008) Phylogenetic relationships of butterflies of the
tribe Acraeini (Lepidoptera, Nymphalidae, Heliconiinae) and the
evolution of host plant use. Mol Phylogenet Evol 46: 515--531.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2007.11.024}{10.1016/j.ympev.2007.11.024}.

@@

43. Brower AVZ, Freitas AVL, Lee M-M, Silva-Brand\~ao KL, Whinnett A, et
al. (2006) Phylogenetic relationships among the Ithomiini (Lepidoptera:
Nymphalidae) inferred from one mitochondrial and two nuclear gene
regions. Syst Entomol 31: 288--301.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2006.00321.x}{10.1111/j.1365-3113.2006.00321.x}.
